### 2022-07-30 thesis/bern_prune_deg_output.tex
Second draft of thesis finished

\begin{verbatim}
            -----------------------------------
            Computing Step 0
            ------------------------------------

            BASE VERTEX: [0.005, 2.0]
            GENERATORS: [[-0.004, 0.0], [0.0, -0.004999999999999893]]

            ------------------------------------
            Stats for Template Direction: [1. 0.]
            ------------------------------------

            Chosen Max Monom Deg: (0, 1),  Chosen Min Monom Deg: (0, 0)

            Actual Max Monom Deg: (0, 0), Actual Min Monom Def: (1, 1)

            Actual Bernstein degree: [1, 1]

            Actual Functional Comp Poly: -0.004*x - 0.000499999999999989*y + 0.205
            Returned set of Maximum Monom from Lookup Table:

            [((0, 1), 0.204500000000000),
             ((1, 0), 0.201000000000000),
             ((1, 1), 0.200500000000000)]

            Returned set of Minimum Monom from Lookup Table:
            [((0, 0), 0.205000000000000)]

            Returned set of ALL Actual Monomials and their ALL Computed Acutal Bernstein Coeff:
            [((0, 0), 0.20500000000000002),
             ((0, 1), 0.20450000000000002),
             ((1, 0), 0.201),
             ((1, 1), 0.2005)]

            Difference between Queried Max Coeff and Actual Max Coeff: -0.000500000000000000

            Difference between Queried Min Coeff and Actual Min Coeff: 0.00450000000000000

            ------------------------------------
            Stats for Template Direction: [0. 1.]
            ------------------------------------

            Chosen Max Monom Deg: (3, 3),  Chosen Min Monom Deg: (0, 0)

            Actual Max Monom Deg: (2, 0), Actual Min Monom Def: (0, 1)

            Actual Bernstein degree: [2, 1]

            Actual Functional Comp Poly: 0.0004*x - 0.00499999999999989*y + 0.1*(1 - 2.5e-5*(1 - 0.8*x)**2)*(2.0 - 0.00499999999999989*y) + 1.9995
            Returned set of Maximum Monom from Lookup Table:

            [((3, 3), 2.18359741950000)]

@@

            Returned set of ALL Actual Monomials and their ALL Computed Acutal Bernstein Coeff:
            [((0, 0), 2.199495),
             ((0, 1), 2.1939950125000003),
             ((1, 0), 2.1996990000000003),
             ((1, 1), 2.1941990025000004),
             ((2, 0), 2.1998998000000003),
             ((2, 1), 2.1943998005000007)]

@@

            Difference between Queried Min Coeff and Actual Min Coeff: 0.00549998749999991
  \end{verbatim}

>>>>

\begin{figure}
\begin{verbatim}
    -----------------------------------
              Computing Step 0
    -----------------------------------

    BASE VERTEX: [0.005, 2.0]
    GENERATORS: [[-0.004, 0.0], [0.0, -0.0049999999999999]]
    ....
    ....
    -------------------------------------
    Stats for Template Direction: [0. 1.]
    -------------------------------------

    Queried Max Monom Deg: (3, 3)
    Queried Min Monom Deg: (0, 0)

    Actual Max Monom Deg: (2, 0)
    Actual Min Monom Def: (0, 1)

    Actual Composed Poly:
    0.0004*x - 0.00499999999999989*y
    + 0.1*(1 - 2.5e-5*(1 - 0.8*x)**2)*(2.0 - 0.00499999999999989*y)
    + 1.9995

    Total Poly Degree: [2, 1]

    Returned set of Maximum Monom from Lookup Table:
    [((3, 3), 2.18359741950000)]

@@

    Set of ALL basis degrees and true Bernstein coeffs:
    [((0, 0), 2.199495),
     ((0, 1), 2.1939950125000003),
     ((1, 0), 2.1996990000000003),
     ((1, 1), 2.1941990025000004),
     ((2, 0), 2.1998998000000003),
     ((2, 1), 2.1943998005000007)]

@@

    Difference between Queried Min Coeff and Actual Min Coeff:
    0.00549998749999991
  \end{verbatim}
  \caption{Output for First step of Reachability algorithm with the Vanderpol Model.}
  \label{fig:bern_prune_deg_output}
\end{figure}

### 2022-07-30 thesis/bern_prune_wrapping_error.tex
Second draft of thesis finished

\begin{verbatim}
------------------------------------
Computing Step 3
------------------------------------

------------------------------------
Stats for Template Direction: [1. 0.]
------------------------------------

Chosen Max Monom Deg: (1, 1),  Chosen Min Monom Deg: (0, 0)

Actual Max Monom Deg: (1, 1), Actual Min Monom Deg: (0, 0)

Actual Bernstein degree: [1, 1]

Actual Sympy Poly: 0.007306445824668*x + 0.0111954493962119*y + 0.906973678980699
Returned set of Maximum Monom from lookup_table:

[((1, 1), 0.925475574201579)]

Returned set of Minimum Monom from lookup_table:
[((0, 0), 0.906973678980699)]

Returned set of ALL Monomials and their ALL Computed Actual Bernstein Coeff:
[((0, 0), 0.906973678980699),
 ((0, 1), 0.9181691283769109),
 ((1, 0), 0.914280124805367),
 ((1, 1), 0.9254755742015789)]

Difference between Queried Max Coeff and Actual Max Coeff: 0

Difference between Queried Min Coeff and Actual Min Coeff: 0

@@

Chosen Max Monom Deg: (0, 3),  Chosen Min Monom Deg: (0, 0)

Actual Max Monom Deg: (0, 1), Actual Min Monom Def: (2, 0)

Actual Bernstein degree: [2, 1]

Actual Sympy Poly: -0.0007306445824668*x + 0.111954493962119*y + 0.1*(1 - 0.435728408759507*(0.0110687411271527*x + 1)**2)*(0.111954493962119*y + 2.46876406785527) + 2.40275434063576

Returned set of Maximum Monom from lookup_table:

[((1, 2), 2.77693923047705),
 ((2, 1), 2.65709768697245),
 ((3, 1), 2.65546013926846),
 ((0, 2), 2.77860321954750),
 ((2, 2), 2.77526086680021),
 ((3, 2), 2.77356812851698),
 ((1, 3), 2.89515700322449),
 ((1, 1), 2.65872145772961),
 ((0, 3), 2.89687498755508),
 ((2, 0), 2.53893450714470),
 ((3, 0), 2.53735215001995),
 ((2, 3), 2.89342404662796),
 ((3, 3), 2.89167611776549)]

Returned set of Minimum Monom from lookup_table:
[((0, 0), 2.54205968353236)]

Returned set of ALL Monomials and their ALL Computed Actual Bernstein Coeff:
[((0, 0), 2.542059683532361),
 ((0, 1), 2.6603314515399323),
 ((1, 0), 2.5405036849821685),
 ((1, 1), 2.658721457729609),
 ((2, 0), 2.5389345071447),
 ((2, 1), 2.657097686972454)]

Difference between Queried Max Coeff and Actual Max Coeff: 0.236543536015143

Difference between Queried Min Coeff and Actual Min Coeff: 0.00312517638766119

------------------------------------
Computing Step 4
------------------------------------

------------------------------------
Stats for Template Direction: [1. 0.]
------------------------------------

Chosen Max Monom Deg: (1, 1),  Chosen Min Monom Deg: (0, 0)\ n
Actual Max Monom Deg: (0, 0), Actual Min Monom Def: (1, 1)

Actual Bernstein degree: [1, 1]

Actual Sympy Poly: -0.0185018952208799*x - 0.0354815304022714*y + 1.21516307295709
Returned set of Maximum Monom from lookup_table:

[((1, 1), 1.16117964733394)]

Returned set of Minimum Monom from lookup_table:
[((0, 0), 1.21516307295709)]

Returned set of ALL Monomials and their ALL Computed Actual Bernstein Coeff:
[((0, 0), 1.2151630729570864),
 ((0, 1), 1.1796815425548148),
 ((1, 0), 1.1966611777362064),
 ((1, 1), 1.161179647333935)]

Difference between Queried Max Coeff and Actual Max Coeff: -0.0539834256231513

Difference between Queried Min Coeff and Actual Min Coeff: 0.0539834256231513

Chosen Max Monom Deg: (3, 0),  Chosen Min Monom Deg: (0, 3)\ n
Actual Max Monom Deg: (2, 0), Actual Min Monom Def: (0, 1)

Actual Bernstein degree: [2, 1]

Actual Sympy Poly: 0.00185018952208799*x - 0.354815304022714*y + 0.1*(1 - 0.856505038443742*(1 - 0.0199917704331005*x)**2)*(2.89687498755508 - 0.354815304022714*y) + 2.80432743013492

Returned set of Maximum Monom from lookup_table:

[((0, 1), 2.48598940176842),
 ((1, 2), 2.13075300161303),
 ((2, 1), 2.49645813555339),
 ((3, 1), 2.50156197271691),
 ((0, 2), 2.12608267690468),
 ((2, 2), 2.13534845254406),
 ((1, 0), 2.85178155552809),
 ((3, 2), 2.13986902969777),
 ((1, 3), 1.77023872465550),
 ((1, 1), 2.49126727857056),
 ((0, 3), 1.76617595204093),
 ((2, 0), 2.85756781856273),
 ((3, 0), 2.86325491573606),
 ((2, 3), 1.77423876953473),
 ((3, 3), 1.77817608667862)]

@@

Returned set of ALL Monomials and their ALL Computed Actual Bernstein Coeff:
[((0, 0), 2.8458961266321676),
 ((0, 1), 2.485989401768422),
 ((1, 0), 2.8517815555280945),
 ((1, 1), 2.491267278570564),
 ((2, 0), 2.8575678185627256),
 ((2, 1), 2.496458135553395)]

@@

Difference between Queried Min Coeff and Actual Min Coeff: -0.719813449727491
\end{verbatim}

>>>>

\begin{figure}
\begin{verbatim}
------------------------------------
Computing Step 4
------------------------------------

@@

Chosen Max Monom Deg: (3, 0)
Chosen Min Monom Deg: (0, 3)
...
Returned set of Maximum Monom from lookup_table:
[((0, 1), 2.48598940176842),
 ((1, 2), 2.13075300161303),
 ((2, 1), 2.49645813555339),
 ((3, 1), 2.50156197271691),
 ((0, 2), 2.12608267690468),
 ((2, 2), 2.13534845254406),
 ((1, 0), 2.85178155552809),
 ((3, 2), 2.13986902969777),
 ((1, 3), 1.77023872465550),
 ((1, 1), 2.49126727857056),
 ((0, 3), 1.76617595204093),
 ((2, 0), 2.85756781856273),
 ((3, 0), 2.86325491573606),
 ((2, 3), 1.77423876953473),
 ((3, 3), 1.77817608667862)]

@@

@@

Difference between Queried Min Coeff and Actual Min Coeff: -
0.719813449727491
\end{verbatim}

\caption{Example of Wrapping Error Obstacle demonstrated for Step 4 for Vanderpol Model.}
\label{fig:bern_prune_wrapping_output}
\end{figure}

### 2022-07-30 thesis/conclusion.tex
Second draft of thesis finished

\chapter{Conclusion}
\label{chap:conclusion}
In this paper, we investigated two techniques for generating templates dynamically: first using linear approximation of the dynamics, and second using PCA.
%
We demonstrated that these techniques improve the accuracy of reachable set by an order of magnitude when compared to static or random template directions.
%
We also observed that both these techniques improve the accuracy of the reachable sets for different benchmarks.
%
In future, we intend to investigate Koopman linearization techniques for computing alternative linear approximation template directions \cite{bak2021reachability}.
%
We also wish to investigate the use of a massively-parallel implementation using HPC hardware such as GPUs for optimizing over an extremely large number of parallelotopes and their template directions. This is inspired by the approach behind the recent tool \emph{PIRK} \cite{devonport2020pirk}.

>>>>

\chapter{Conclusion}
\label{chap:conclusion}
In this thesis, we covered a specific technique to perform reachability analysis over non-linear dynamical systems by leveraging parallelotope bundles and a specific non-linear optimization problem whose solutions determine certain template directions' offsets required to express the reachable set.
%
We presented the original algorithm utilizing static template directions.
%
We then investigated two techniques for generating templates \emph{dynamically}: first using linear approximation of the dynamics, and second using PCA.
%
We demonstrated that these techniques improve the accuracy of reachable set by an order of magnitude when compared to static or random template directions.
%
We also observed that both these techniques improve the accuracy of the reachable sets for different benchmarks.
%
Finally, we experimented with potential applications of the Bernstein expansion technique to real-time reachability. We found that several hurdles and barriers arise to effectively utilizing the pruning method developed in the pre-computation phase.
%
Several remarks on ideas towards improvement of the methods we developed are listed below:
\begin{enumerate}
  \item Koopman linearization techniques for computing alternative linear approximation template directions with alternative optimization methods could yield interesting modifications to Algorithms \ref{alg:old} and \ref{alg:new} \cite{bak2021reachability}.

  \item The use of a massively-parallel implementation using HPC hardware, such as GPUs, for optimizing over an extremely large number of parallelotopes and their template directions is also an immediate extension. This is inspired by the approach behind the recent tool \emph{PIRK} \cite{devonport2020pirk}.

  \item Step five of the pre-computation algorithm, where it simply takes the intervals which dominate all the other intervals, may be too crude to properly yield a proper speed-up. Are there any other methods of adding basis monomials to the lookup table which take into account the degree discrepancies outlined in Section \ref{sec:deg_disc}?
\end{enumerate}

%

### 2022-07-30 thesis/frontmatter/abstract.tex
Second draft of thesis finished

\end{center}
\par Reachable set computation is an important technique for the verification of safety properties of dynamical systems.
%
% one method proposed for solving this problem, based on parallelotope bundle reachability for
%
In this thesis, we investigate reachable set computation for discrete nonlinear systems based on parallelotope bundles.
%
The crux of the reachability algorithm relies on computing an upper and lower bound on the supremum and infimum respectively of a nonlinear function over a rectangular domain.
%
We cover two ways of computing these bounds: one method utilizing Bernstein polynomials and the other relying on a non-linear optimization tool developed by NASA, Kodiak.
%
We aim to improve the traditional parallelotope-based reachability method by removing the manual step of parallelotope template selection in order to make the procedure fully automatic.
%
Furthermore, we show that adding templates dynamically during computations can improve accuracy.
%
% One of the simplest algorithms for computing reachable sets for discrete nonlinear systems uses parallelotope bundles and Bernstein polynomials.
%
%Our main hypothesis in this paper is that generating templates in a dynamic manner would improve the accuracy of the reachable set.
%
To this end, we investigate two techniques for generating the template directions.
%
The first technique approximates the dynamics as a linear transformation and generates templates using this linear transformation.
%
The second technique uses Principal Component Analysis (PCA) of sample trajectories for generating templates.
%
We have implemented our approach in a Python-based tool called Kaa.
%
%Kaa was developed as a more compact, simple implementation of the pre-existing parallelotope-based reachability tool, Sapo.
%
% have implemented two main enhancements to it.
%
The tool is modular and use two types of global optimization solvers, the first using Bernstein polynomials and the second using
the aforementioned Kodiak library.
%
Additionally, we leverage the natural parallelism of the reachability algorithm and parallelize the Kaa implementation.
%
Finally, we demonstrate the improved accuracy of our approach on several standard nonlinear benchmark systems, including a high-dimensional COVID19 model proposed by the Indian Supermodel Committee.

\clearpage

>>>>

\end{center}
\par Reachable set computation is an important technique for the verification of safety properties of dynamical systems.
%
% one method proposed for solving this problem, based on parallelotope bundle reachability for
%
In this thesis, we investigate reachable set computation for discrete nonlinear systems based on parallelotope bundles.
%
The crux of the reachability algorithm relies on computing an upper and lower bound on the supremum and infimum respectively of a nonlinear function over a rectangular domain.
%
We cover two ways of computing these bounds: one method utilizing Bernstein polynomials and the other relying on a non-linear optimization tool developed by NASA, Kodiak.
%
We aim to improve the traditional parallelotope-based reachability method by removing the manual step of parallelotope template selection in order to make the procedure fully automatic.
%
Furthermore, we show that adding templates dynamically during computations can improve accuracy.
%
% One of the simplest algorithms for computing reachable sets for discrete nonlinear systems uses parallelotope bundles and Bernstein polynomials.
%
%Our main hypothesis in this paper is that generating templates in a dynamic manner would improve the accuracy of the reachable set.
%
To this end, we investigate two techniques for generating the template directions.
%
The first technique approximates the dynamics as a linear transformation and generates templates using this linear transformation.
%
The second technique uses Principal Component Analysis (PCA) of sample trajectories for generating templates.
%
We have implemented our approach in a Python-based tool called Kaa.
%
%Kaa was developed as a more compact, simple implementation of the pre-existing parallelotope-based reachability tool, Sapo.
%
% have implemented two main enhancements to it.
%
The tool is modular and use two types of global optimization solvers, the first using Bernstein polynomials and the second using
the aforementioned Kodiak library.
%
We demonstrate the improved accuracy of our approach on several standard nonlinear benchmark systems, including a high-dimensional COVID19 model proposed by the Indian Supermodel Committee.
%
Finally, we explore a particular potential application of the Bernstein expansion technique to real-time reachability.
%
We present evidence of several hurdles and barriers against effectively utilizing our Bernstein coefficient pruning method.
\clearpage

### 2022-07-30 thesis/prelim.tex
Draft of RT reachability written
Second draft of thesis finished

Examples of prominent non-linear dynamical systems include the Lotka-Volterra predator-prey model \cite{wangersky1978lotka}, the Fitz-Hugh Neuron model \cite{fitzhugh1961impulses}, and the recently introduced COVID19 disease model \cite{indiansuper2020supermodel}. Throughout this thesis, we discretize any continuous dynamics through the well-known Euler method. Thus, up to some error term of bounded degree, we can turn any non-linear system into the form given by Equation~\ref{eq:sys}.
%
\begin{example}
The SIR Epidemic model is a 3-dimensional dynamical system governed by the following continuous dynamics:
\begin{align} \label{eqn:sir}
    \begin{cases}
        s' &= \beta \cdot s i \\
        i' &= \beta \cdot s i - \gamma \cdot i \\
        r' &= \gamma \cdot i
    \end{cases}
\end{align}
where $s,i,r$ represent the fractions of a population of individuals designated as \textit{susceptible}, \textit{infected}, and \textit{recovered} respectively. There are two parameters, namely $\beta$ and $\gamma$, which influence the evolution of the system. $\beta$ is labeled as the \emph{contraction rate} and $1/\gamma$ is the \emph{mean infective period}.
%
Discretizing Equation~\ref{eqn:sir} according the Euler method yields the dynamics:

@@

%-----------------------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{Bernstein Polynomials}
\label{sec:bernstein}
In this section, we define Bernstein polynomials and state some of their enclosure properties. A \emph{multi-index} ${\bf i}$ of length $n$ is defined as tuple of $n$ elements ${\bf i} = (i_1,\cdots, i_n)$ such that each $i_k \in \mathbb{N}$. Furthermore, we order the multi-indices as follows: if ${\bf i}$ and ${\bf j}$ are two multi-indices of length $n$, then
\[
  {\bf i} \leq {\bf j} \iff i_k \leq j_k, \quad 1 \leq  k \leq n
\]
Finally, we generalize the product of binomial coefficients as:
\[
  \binom{\boldi}{\boldj} := \prod_{k=1}^n \binom{i_k}{j_k}
\]
%
Given two multi-indices $\boldi$ and $\boldd$ of size $n$, where $\boldi \leq \boldd$, the Bernstein basis polynomial of degree $\boldd$ and index $\boldi$ is defined as:
\begin{equation}
\label{eq:bernstein_basis_poly}
\mathcal{B}_{(\boldi,\boldd)}(\boldx) = \beta_{i_1,d_1}(x_1) \beta_{i_2,d_2}(x_2)\ldots \beta_{i_n,d_n}(x_n).
\end{equation}
%
where for $i,d,x \in \reals$:
%
\begin{equation}
\beta_{i,d}(x) = \binom{d}{i}x^{i}(1-x)^{d - i}
\end{equation}
%
Let $p: \reals^n \rightarrow \reals$ of be a real polynomial of degree at most $\boldd$. We can express $p$ as a linear combination of monomials of degree at most $\boldd$:
\[
p(\boldx) = \sum_{\boldi \leq \boldd} a_\boldi \cdot \boldx^\boldi
\]
where $\boldx^\boldi$ represents the monomial $x_1^{i_1}x_2^{i_2}\cdots x_n^{i_n}$. Every such real polynomial $p$ of degree at most $\boldd$ can be represented as linear combination of Bernstein basis polynomials of of degree $\boldd$:
%
\begin{equation}
  p(\boldx) = \sum_{\boldi \leq \boldd} b_{\boldi} \cdot \mathcal{B}_{(\boldi,\boldd)}(\boldx)
\end{equation}
where $b_\boldi$ denotes the \emph{$\boldi^{th}$ Bernstein Coefficient}:

\begin{equation}
b_{\boldi} = \sum_{\boldj \leq \boldi} \frac{\binom{\boldi}{\boldj}}{\binom{\boldd}{\boldj}}\cdot a_{\boldj}
\end{equation}
%
\noindent In other words, given a polynomial $p(x_1,\ldots,x_n) = \sum_{j \in J} a_j {\bf x}_{j}$ where $J$ is a set of multi-indices iterating through the degrees found in $p$ with $a_j \in \mathbb{R}$, then $p(x_1,\ldots,x_n)$ can be converted into its counterpart under the Bernstein basis, $p(x_1,\ldots,x_n) = \sum_{j \in J} b_j \mathcal{B}_j $ where $b_j$ are the corresponding Bernstein coefficients.
%
%\begin{property}
%\label{prop:basis_property}

%The Bernstein basis polynomials $\$
%\end{property}

The primary advantage of the Bernstein representation of a polynomial $p(x_1,...,x_n)$ is that an upper bound on the supremum and lower bound on the infimum of $p(x_1,...,x_n)$ in $[0,1]^{n}$ can be computed purely by observing the coefficients of the polynomial in the Bernstein basis. Specifically, the upper and lower bounds of $p(x_1,\ldots,x_n)$ over $[0,1]^n$ are bounded by the Bernstein coefficients. We state this as a property without proof.
%
\begin{property} (Enclosure Property)
  \label{prop:bern_enclosure}
  Let $p: \reals^n \rightarrow \reals$ be a real mutlivarite polynomial of degree $\boldd$, and let $p(\boldx) = \sum_{\boldi \leq \boldd} b_\boldi \cdot \mathcal{B}_{(\boldi,\boldd)}(\boldx)$ be the Bernstein expansion of $p$, then
  $$
  \min_{\boldi \leq \boldd} \{b_\boldi\} ~~\leq~~ \inf_{x \in [0,1]^n} p(x) ~~~~~\leq~~~~ \sup_{x \in [0,1]^{n}} p(x) ~~\leq~~ \max_{\boldi \leq \boldd} \{b_\boldi\}
  $$
\end{property}

>>>>

Examples of prominent non-linear dynamical systems include the Lotka-Volterra predator-prey model \cite{wangersky1978lotka}, the Fitz-Hugh Neuron model \cite{fitzhugh1961impulses}, and the recently introduced COVID19 disease model \cite{indiansuper2020supermodel}. Throughout this thesis, we discretize any continuous dynamics through the well-known Euler method. Thus, up to some error term of bounded degree, we can turn any non-linear system into the form given by Equation~\ref{eq:sys}.
%
\begin{example}
\label{ex:sir}
The SIR Epidemic model is a 3-dimensional dynamical system governed by the following continuous dynamics:
\begin{align} \label{eqn:sir}
    \begin{cases}
        s' &= \beta \cdot s i \\
        i' &= \beta \cdot s i - \gamma \cdot i \\
        r' &= \gamma \cdot i
    \end{cases}
\end{align}
where $s,i,r$ represent the fractions of a population of individuals designated as \textit{susceptible}, \textit{infected}, and \textit{recovered} respectively. There are two parameters, namely $\beta$ and $\gamma$, which influence the evolution of the system. $\beta$ is labeled as the \emph{contraction rate} and $1/\gamma$ is the \emph{mean infective period}.
%
Discretizing Equation~\ref{eqn:sir} according the Euler method yields the dynamics:

@@

%--------------------------------------------------------------------------------------------------------------------------------------------------------- --------
\subsection{Bernstein Polynomials}
\label{sec:bernstein}
In this section, we define Bernstein polynomials and state some of their enclosure properties. A \emph{multi-index} ${\bf i}$ of length $n$ is defined as tuple of $n$ elements ${\bf i} = (i_1,\cdots, i_n)$ such that each $i_k \in \mathbb{N}$. Furthermore, we order the multi-indices as follows: if ${\bf i}$ and ${\bf j}$ are two multi-indices of length $n$, then
\[
  {\bf i} \leq {\bf j} \iff i_k \leq j_k, \quad 1 \leq  k \leq n
\]
Finally, we generalize the product of binomial coefficients as:
\[
  \binom{\boldi}{\boldj} := \prod_{k=1}^n \binom{i_k}{j_k}
\]
%
Given two multi-indices $\boldi$ and $\boldd$ of size $n$, where $\boldi \leq \boldd$, the Bernstein basis polynomial of degree $\boldd$ and index $\boldi$ is defined as:
\begin{equation}
\label{eq:bernstein_basis_poly}
\mathcal{B}_{(\boldi,\boldd)}(\boldx) = \beta_{i_1,d_1}(x_1) \beta_{i_2,d_2}(x_2)\ldots \beta_{i_n,d_n}(x_n).
\end{equation}
%
where for $i,d,x \in \reals$:
%
\begin{equation}
\beta_{i,d}(x) = \binom{d}{i}x^{i}(1-x)^{d - i}
\end{equation}
%
Let $p: \reals^n \rightarrow \reals$ of be a real polynomial of degree at most $\boldd$. We can express $p$ as a linear combination of monomials of degree at most $\boldd$:
\[
p(\boldx) = \sum_{\boldi \leq \boldd} a_\boldi \cdot \boldx^\boldi
\]
where $\boldx^\boldi$ represents the monomial $x_1^{i_1}x_2^{i_2}\cdots x_n^{i_n}$. One of the most important properties of Berstein polynomials is that the Bernstein basis polynomials of degree $\boldd$ span the vector space of real multivariate polynomials of degree at most $\boldd$:

\begin{property}
\label{prop:bern_basis}
Every real polynomial $p$ of degree at most $\boldd$ can be represented as linear combination of Bernstein basis polynomials of degree $\boldd$:
%
\begin{equation}
  \label{eq:bernstein_coeff}
  p(\boldx) = \sum_{\boldi \leq \boldd} b_{\boldi} \cdot \mathcal{B}_{(\boldi,\boldd)}(\boldx)
\end{equation}
where $b_\boldi$ denotes the \emph{$\boldi^{th}$ Bernstein Coefficient}:

\begin{equation}
b_{\boldi} = \sum_{\boldj \leq \boldi} \frac{\binom{\boldi}{\boldj}}{\binom{\boldd}{\boldj}}\cdot a_{\boldj}
\end{equation}
\end{property}

\noindent In other words, given a polynomial $p(x_1,\ldots,x_n) = \sum_{j \in J} a_j {\bf x}_{j}$ where $J$ is a set of multi-indices iterating through the degrees found in $p$ with $a_j \in \mathbb{R}$, then $p(x_1,\ldots,x_n)$ can be converted into its counterpart under the Bernstein basis, $p(x_1,\ldots,x_n) = \sum_{j \in J} b_j \mathcal{B}_j $ where $b_j$ are the corresponding Bernstein coefficients.

The primary advantage of the Bernstein representation of a polynomial $p(x_1,...,x_n)$ is that an upper bound on the supremum and lower bound on the infimum of $p(x_1,...,x_n)$ in $[0,1]^{n}$ can be computed purely by observing the coefficients of the polynomial in the Bernstein basis. Specifically, the upper and lower bounds of $p(x_1,\ldots,x_n)$ over $[0,1]^n$ are bounded by the Bernstein coefficients. We state this as a property without proof.

\begin{property} (Enclosure Property)
  \label{prop:bern_enclosure}
  Let $p: \reals^n \rightarrow \reals$ be a real multivariate polynomial of degree $\boldd$, and let $p(\boldx) = \sum_{\boldi \leq \boldd} b_\boldi \cdot \mathcal{B}_{(\boldi,\boldd)}(\boldx)$ be the Bernstein expansion of $p$, then
  $$
  \min_{\boldi \leq \boldd} \{b_\boldi\} ~~\leq~~ \inf_{x \in [0,1]^n} p(x) ~~~~~\leq~~~~ \sup_{x \in [0,1]^{n}} p(x) ~~\leq~~ \max_{\boldi \leq \boldd} \{b_\boldi\}
  $$
\end{property}
